### 2009-11-13 doc/manuals/hopi/hopi-manual.tex
very-very basic manual about hopi and echo - what else should go in these?

%%%%---- The title ----
{\centering \textsc{\Large The Echo Service - The Missing Manual}\Large \par}
\vspace*{0.5cm}

@@

\section{Introduction} % (fold)
\label{sec:introduction}
The capability of the echo service is to accept SOAP messages like this:
\begin{verbatim}
<?xml version="1.0"?>
<soap-env:Envelope
	xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:echo="urn:echo">
    <soap-env:Body>
        <echo:echo>
            <echo:say>HELLO</echo:say>
        </echo:echo>
    </soap-env:Body>
</soap-env:Envelope>
\end{verbatim}
Then the Echo service adds a prefix and a suffix to the message and sends it back like this:
\begin{verbatim}
<?xml version="1.0"?> 
<soap-env:Envelope
	xmlns:echo="urn:echo" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/">
    <soap-env:Body>
        <echo:echoResponse>
            <echo:hear>hi!}}</echo:hear>
        </echo:echoResponse>
    </soap-env:Body>
</soap-env:Envelope>
\end{verbatim}
There are a C++ and a Python implementation of the Echo service, and there are configuration profiles for secure and non-secure deployments for both languages.
% section introduction (end)

\section{Clients} % (fold)
\label{sec:clients}
Currently in the nordugrid subversion there are at least two readily available client to test the Echo service:
\begin{itemize}
	\item \textbf{echo\_client.py}\footnote{\url{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/tests/echo/echo_client.py}} is a python script which gets the credentials from the userconfig, and sends a single message to the given URL, then prints the reply
	\item \textbf{perftest}\footnote{\url{http://svn.nordugrid.org/trac/nordugrid/browser/arc1/trunk/src/tests/perf/perftest.cpp}} sends as many messages as possible within a given number of seconds using a given number of threads
\end{itemize}
% section clients (end)

\section{Configuration of the C++ Echo service} % (fold)
\label{sec:configuration}
Here is an example configuration of a secure C++ Echo service:

\begin{verbatim}
<?xml version="1.0"?>
<cfg:ArcConfig xmlns="http://www.nordugrid.org/schemas/loader/2009/08"
	xmlns:cfg="http://www.nordugrid.org/schemas/arcconfig/2009/08"
	xmlns:tcp="http://www.nordugrid.org/schemas/tcp/2009/08"
	xmlns:tls="http://www.nordugrid.org/schemas/tls/2009/08"
	xmlns:echo="http://www.nordugrid.org/schemas/echo/2009/08">
    <cfg:Server>
        <cfg:PidFile>tmp/arched.pid</cfg:PidFile>
        <cfg:Logger>
            <cfg:File>/var/log/arched.log</cfg:File>
            <cfg:Level>ERROR</cfg:Level>
        </cfg:Logger>
    </cfg:Server>
    <ModuleManager>
        <Path inisections="common" initag="libpath">/usr/local/lib/arc/</Path>
    </ModuleManager>
    <Plugins>
        <Name>mcctls</Name>
        <Name>mcchttp</Name>
        <Name>mccsoap</Name>
        <Name>mcctcp</Name>
    </Plugins>
    <Chain>
        <Component name="tcp.service" id="tcp">
            <next id="tls"/>
            <tcp:Listen>
               <tcp:Interface>0.0.0.0</tcp:Interface>
               <tcp:Port>50000</tcp:Port>
               <tcp:Version>4</tcp:Version>
            </tcp:Listen>
        </Component>
        <Component name="tls.service" id="tls">
            <next id="http"/>
            <tls:KeyPath>/etc/grid-security/hostkey.pem</tls:KeyPath>
            <tls:CertificatePath>/etc/grid-security/hostcert.pem</tls:CertificatePath>
            <tls:CACertificatesDir>/etc/grid-security/certificates</tls:CACertificatesDir>
        </Component>
        <Component name="http.service" id="http">
            <next id="soap">POST</next>
            <next id="plexer">GET</next>
            <next id="plexer">PUT</next>
        </Component>
        <Component name="soap.service" id="soap">
            <next id="plexer"/>
        </Component>
        <Plexer name="plexer.service" id="plexer">
            <next id="echo">^/Echo$</next>
        </Plexer>
        <Service name="echo" id="echo">
            <echo:prefix>[</echo:prefix>
            <echo:suffix>]</echo:suffix>
        </Service>
    </Chain>
</cfg:ArcConfig>
\end{verbatim}
% section configuration (end)

\section{Configuration of the Python Echo service} % (fold)
\label{sec:configuration_of_the_python_echo_service}
Here is an example configuration of a secure python Echo service:

\begin{verbatim}
<?xml version="1.0"?>
<cfg:ArcConfig xmlns="http://www.nordugrid.org/schemas/loader/2009/08"
	xmlns:cfg="http://www.nordugrid.org/schemas/arcconfig/2009/08"
	xmlns:tcp="http://www.nordugrid.org/schemas/tcp/2009/08"
	xmlns:tls="http://www.nordugrid.org/schemas/tls/2009/08"
	xmlns:echo="http://www.nordugrid.org/schemas/echo/2009/08"
	xmlns:py="http://www.nordugrid.org/schemas/pythonwrapper/2009/08">
    <cfg:Server>
        <cfg:PidFile>tmp/arched.pid</cfg:PidFile>
        <cfg:Logger>
            <cfg:File>/var/log/arched.log</cfg:File>
            <cfg:Level>ERROR</cfg:Level>
        </cfg:Logger>
    </cfg:Server>
    <ModuleManager>
        <Path inisections="common" initag="libpath">/usr/local/lib/arc/</Path>
    </ModuleManager>
    <Plugins>
        <Name>mcctls</Name>
        <Name>mcchttp</Name>
        <Name>mccsoap</Name>
        <Name>mcctcp</Name>
    </Plugins>
    <Chain>
        <Component name="tcp.service" id="tcp">
            <next id="tls"/>
            <tcp:Listen>
               <tcp:Interface>0.0.0.0</tcp:Interface>
               <tcp:Port>50000</tcp:Port>
               <tcp:Version>4</tcp:Version>
            </tcp:Listen>
        </Component>
        <Component name="tls.service" id="tls">
            <next id="http"/>
            <tls:KeyPath>/etc/grid-security/hostkey.pem</tls:KeyPath>
            <tls:CertificatePath>/etc/grid-security/hostcert.pem</tls:CertificatePath>
            <tls:CACertificatesDir>/etc/grid-security/certificates</tls:CACertificatesDir>
        </Component>
        <Component name="http.service" id="http">
            <next id="soap">POST</next>
            <next id="plexer">GET</next>
            <next id="plexer">PUT</next>
        </Component>
        <Component name="soap.service" id="soap">
            <next id="plexer"/>
        </Component>
        <Plexer name="plexer.service" id="plexer">
            <next id="echo">^/Echo$</next>
        </Plexer>
        <Service name="pythonservice" id="echo">
            <py:ClassName>echo_python.EchoService.EchoService</py:ClassName>
            <echo:prefix>[</echo:prefix>
            <echo:suffix>]</echo:suffix>
        </Service>
    </Chain>
</cfg:ArcConfig>
\end{verbatim}
% section configuration_of_the_python_echo_service (end)

>>>>

%%%%---- The title ----
{\centering \textsc{\Large The Hopi manual}\Large \par}
\vspace*{0.5cm}

@@

\section{Introduction} % (fold)
\label{sec:introduction}
The Hopi service is a HTTP(S) server supporting GET and PUT methods and capable of generating a HTML listing of files. It's main configuration parameter is the document root directory.

It also has a slave mode which is used in the Chelonia storage system tied to the Shepherd service. In the slave mode: 1. there is no HTML listing generated; 2. the files are removed after download; 3. upload is only possible to an existing file, which will be removed after the upload. (The Shepherd service keeps a second hardlink of each file in a separate directory, so that's why it makes sense to remove files after transfer.)

The Hopi service can be the only service in a message chain, in that case it does not need to have a Plexer, and the URLs will not contain any extra path; or the Hopi could be after the Plexer, in that case all the URLs contains a fixed path (e.g. \verb!https://localhost:60000/hopi/!).
% section introduction (end)

\section{Clients} % (fold)
\label{sec:clients}
Because Hopi is a HTTP(S) server, any HTTP client can be used (for HTTPS maybe needs more configuration)
\begin{itemize}
	\item web browser (needs importing the client credentials into the browser)
	\item curl/wget (needs specifying the client credentials as command line argument)
	\item arccp (the client credentials comes from the userconfig)
\end{itemize}
% section clients (end)

\section{Configuration} % (fold)
\label{sec:configuration}
Here is an example configuration of a secure Hopi with Plexer:

\begin{verbatim}
<?xml version="1.0"?>
<cfg:ArcConfig xmlns="http://www.nordugrid.org/schemas/loader/2009/08"
	xmlns:cfg="http://www.nordugrid.org/schemas/arcconfig/2009/08"
	xmlns:tcp="http://www.nordugrid.org/schemas/tcp/2009/08"
	xmlns:tls="http://www.nordugrid.org/schemas/tls/2009/08">
    <cfg:Server>
        <cfg:PidFile>tmp/arched.pid</cfg:PidFile>
        <cfg:Logger>
            <cfg:File>/var/log/arched.log</cfg:File>
            <cfg:Level>ERROR</cfg:Level>
        </cfg:Logger>
    </cfg:Server>
    <ModuleManager>
        <Path>/usr/local/lib/arc/</Path>
    </ModuleManager>
    <Plugins>
        <Name>mcctls</Name>
        <Name>mcchttp</Name>
        <Name>mccsoap</Name>
        <Name>mcctcp</Name>
    </Plugins>
    <Chain>
        <Component name="tcp.service" id="tcp">
            <next id="tls"/>
            <tcp:Listen>
                <tcp:Interface>0.0.0.0</tcp:Interface>
                <tcp:Port>50000</tcp:Port>
                <tcp:Version>4</tcp:Version>
            </tcp:Listen>
        </Component>
        <Component name="tls.service" id="tls">
            <next id="http"/>
            <tls:KeyPath>/etc/grid-security/hostkey.pem</tls:KeyPath>
            <tls:CertificatePath>/etc/grid-security/hostcert.pem</tls:CertificatePath>
            <tls:CACertificatesDir>/etc/grid-security/certificates</tls:CACertificatesDir>
        </Component>
        <Component name="http.service" id="http">
            <next id="soap">POST</next>
            <next id="plexer">GET</next>
            <next id="plexer">PUT</next>
        </Component>
        <Component name="soap.service" id="soap">
            <next id="plexer"/>
        </Component>
        <Plexer name="plexer.service" id="plexer">
            <next id="hopi">^/hopi/</next>
        </Plexer>
        <Service name="hopi" id="hopi">
            <DocumentRoot>/tmp/hopi</DocumentRoot>
            <SlaveMode>0</SlaveMode>
        </Service>
    </Chain>
</cfg:ArcConfig>
\end{verbatim}
% section configuration (end)
